Asymptotic Validity of a Fully Sequential Elimination Procedure for Indifference-Zone Ranking and Selection with Tight Bounds on Probability of Correct Selection

### 2015-04-10 paper/paper_version2.tex
4/10/15

%% LyX 2.0.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\onehalfspacing

@@

@@

\usepackage{babel}
\usepackage{xunicode}
\begin{document}

\title{On the Asymptotic Validity of a Fully Sequential Elimination Procedure
for Indifference-Zone Ranking and Selection with Tight Bounds on Probability
of Correct Selection}

\maketitle
We prove the validity of the sequential elimination IZ procedure proposed
by Frazier \cite{key-5} when $\delta$ goes to $0$. Specifically,
we analyze Algorithm 2, when $B_{1}=\cdots=B_{k}=1$:

\paragraph{Algorithm 2: Discrete-time implementation of BIZ, for unknown and/or heterogeneous variances.}    
\begin{algorithmic}[1]   
\label{alg:hetero-BIZ}   
\REQUIRE $c \in [0,\cmax]$, $\delta>0$, $P^*\in(1/k,1)$, $n_0\ge0$ an integer, $B_1,\ldots,B_k$ strictly positive integers.  Recommended choices are $c=\cmax$, $B_1=\cdots=B_k=1$ and $n_0$ between $10$ and $30$.     If the sampling variances $\lambda^2_x$ are known, replace the estimators     
$\lambdahat^2_{tx}$ with the true values $\lambda^2_x$, and set $n_0=0$.     
To compute $\qhat_{tx}(A)$, use \begin{equation}   q'_{t,x}(A) =    \exp\left(\gamma \delta Y'_{tx}\right) \bigg/ \sum_{x'\in A} \exp\left(\gamma \delta Y'_{tx'}\right)   = \exp\left(\frac{\delta}{\lambda^2_x} Y_{n_x(t),x}\right) \bigg/ \sum_{x'\in A} \exp\left(\frac{\delta}{\lambda^2_{x'}} Y_{n_x'(t),x'}\right), \end{equation}   
where $Y_{n_x(t),x}$ is the sum of the first $n_x(t)$ samples.

\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.     
\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$, $t \leftarrow 1$.
\WHILE{$x\in\mbox{max}_{x\in A}\qhat_{tx}(A)<P$}
\WHILE{$\mbox{min}_{x\in A} \qhat_{tx}(A) \le c$}
 \STATE Let $x\in\mbox{arg min}_{x\in A}\qhat_{tx}(A)$.
    \STATE Let $\upthresh \leftarrow \upthresh/(1-\qhat_{tx}(A))$.     
\STATE Remove $x$ from $A$.
\ENDWHILE
  \STATE Let $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.     
\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.     \STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.  Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.    
\STATE Increment $t$.
 \ENDWHILE
  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} W_{tx} / n_{tx}$ as our estimate of the best.

@@

This paper is organized as follows: In $\text{§}2$, we present the
proof of the validity of the algorithm when the variances are known.
In $\text{§}3$, we prove the case when the variances are unknown.

To prove the case when the variances are known, we use a Functional
Central Limit Theorem that shows how to standardize the output data
to make them behave like Brownian motion processes in the limit. We
also use an extension of the Continuous Mapping Theorem (Theorem 5.5
of Billingsley 1968) to see that the algorithm behaves like a sequential
elimination IZ procedure with a Brownian motion process instead of
the standardize of the sum of the output data in the limit. Finally,
we use the results of the paper of Frazier \cite{key-5} to prove
the validity of this algorithm in the limit.

@@

Without loss of generality, suppose that the true means of the systems
are indexed so that $\mu_{k}\geq\mu_{k-1}\geq\cdots\geq\mu_{1}$.
We suppose that samples from system $x\in\left\{ 1\ldots,k\right\} $
are identically distributed and independent, over time and across
alternatives. We also define $\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$.
We suppose that $\mbox{min}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}>0$
and $c\neq1/k$.

Now we are going to see that the standardize of the sum of the output
data converges to a Brownian motion in $D[0,\infty)$, which is the
set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$ that
are right-continuous and have left-hand limits, with the Skorohod
topology. The Skorohod metric $d_{t}$ on $D\left[0,t\right]$ is:
\[
d_{t}\left(X,Y\right)=\mbox{inf}_{\lambda\in\Lambda_{t}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert X-Y\circ\lambda\right\Vert \right\} 
\]
where $\Lambda_{t}$ is the set of strictly increasing, continuous
mappings of $\left[0,t\right]$ onto itself, and $\left\Vert \cdot\right\Vert $
is the uniform norm, and $I$ is the identity map. Note that uniform
convergence on $\left[0,t\right]$ implies Skorohod convergence.

For $X\in D\left[0,\text{\ensuremath{\infty}}\right)$, let $X^{m}$
be the element of $D[0,\infty)$ defined by
\[
X^{m}\left(t\right)=g_{m}\left(t\right)X\left(t\right)
\]
where 
\[
g_{m}\left(t\right)=\begin{cases}
1 & \mbox{if }t\leq m-1,\\
m-t & \mbox{if }m-1\leq t\leq m,\\
0 & \mbox{if }t\geq m.
\end{cases}
\]
And now take
\[
d_{\infty}\left(X,Y\right)=\sum_{m=1}^{\infty}2^{-m}\left(1\wedge d_{m}\left(X,Y\right)\right)
\]
which is the Skorohod metric on $D\left[0,\infty\right)$.

@@

If $x\in\left\{ 1\ldots,k\right\} $, then
\[
C_{x}\left(\delta,\cdot\right):=\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\right),x}-\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right)
\]
in the sense of $D[0,\infty)$, where $Y_{n,x}$ is the sum of the
first $n$ samples and $W_{x}$ is a standard Brownian motion.

@@

By the Theorem 19.1 of Billingsley 1999 and the sandwich theorem,
\[
\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right).
\]

Since $\frac{\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}-ceil\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right)}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\rightarrow0$
uniformly on $[0,r]$ for every $r$, then it also converges to $0$
on $D[0,\infty)$ and so 
\[
\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right).
\]

Observe that for $\epsilon>0$ and $\delta$ sufficiently small
\[
\left|\frac{-Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right),x}+Y_{\mbox{ceil}\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right),x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\right|<\epsilon\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}+2\right)
\]
and then 
\[
C_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right).
\]

@@

Now we are going to define new algorithms that are almost the same
than the one proposed by Frazier, but instead of $q_{tx}^{\delta}\left(A\right)$,
these algorithms use new functions $q_{tx}^{Y,\delta}\left(A\right)$
which depend on a function $Y$ that is in $D\left[0,\infty\right)^{k}$.

First we are going to suppose that $\delta>0$ and $\mu_{k}=\delta$,$\mu_{k-1}=\cdots=\mu_{\text{1}}=0$.

Let$ $ $Y\in D\left[0,\infty\right)^{k}$ , we define
\begin{eqnarray*}
q_{tx}^{Y,\delta}\left(A\right): & = & \mbox{exp}\left(\frac{Y_{x}\left(t\right)}{\lambda_{z}}+\delta^{2}\beta_{t\frac{1}{\delta^{2}}}I_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{Y_{x^{'}}\left(t\right)}{\lambda_{z}}+\delta^{2}\beta_{t\frac{1}{\delta^{2}}}I_{\left\{ x^{'}=k\right\} }\right)
\end{eqnarray*}
where $\beta_{t\frac{1}{\delta^{2}}}=\frac{\left(n_{0}+t\frac{1}{\delta^{2}}\right)}{\lambda_{z}^{2}}$.

>>>>

%% LyX 2.1.2.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\onehalfspacing

@@

\date{}

@@

\usepackage{babel}
\begin{document}

\title{Asymptotic Validity of a Fully Sequential Elimination Procedure for
Indifference-Zone Ranking and Selection with Tight Bounds on Probability
of Correct Selection}

\author{Saul Toscano\\
{\small{}School of Operations Research and Information Engineering,
Cornell University}\\
Peter I. Frazier\\
{\small{}School of Operations Research and Information Engineering,
Cornell University}}

\maketitle
We consider the indifference-zone (IZ) formulation of the ranking
and selection problem. Conservatism leads classical IZ procedures
to take too many samples in problems with many alternatives. The Bayes-inspired
Indifference Zone (BIZ) procedure, proposed in Frazier (2014), is
less conservative than previous procedures, but its proof of validity
requires strong assumptions. In this paper, we present a new proof
of asymptotic validity that relaxes these assumptions.

One common problem in simulation is that of choosing the best among
several simulated systems. The problem of deciding how many samples
to use from each alternative to support our selection as the best
is the ranking and selection problem. An efficient solution to this
problem has to balance between the time spent simulating and the quality
of the selection.

This paper will consider the indifference-zone (IZ) formulation of
the ranking and selection problem, in which we choose the best system
with probability larger than a pre-specified threshold, whenever the
distance between the best system and the others is sufficiently large.
We say that a sampling procedure having this property satisfies the
IZ guarantee and the set of system configurations under which the
best alternative is better than the second best by at least some given
$\delta>0$ is called the preference zone (PZ). The seminal work dates
back to Bechhofer (1954), with early work compiled in the monograph
Bechhofer et al. (1968). The progress in the area has been summarized
in Bechhofer et al. (1995), Swisher et al. (2003), Kim and Nelson
(2006, 2007) and Frazier (2014).

The goal of an IZ algorithm is to take as few samples as possible
while the IZ guarantee is satisfied. The first IZ procedures presented
in Bechhofer (1954), Paulson (1964), Fabian (1974), Rinott (1978),
Hartmann (1988, 1991), Paulson (1994) satisfy the IZ guarantee, but
they usually take too many samples when there are many alternatives,
in part because their probability of correct selection (PCS) is much
larger than the probability specified by the user. A reason of this
is the use of the Bonferroni's inequality which leads to sample more
than necessary. More recent algorithms in Kim and Nelson (2001), Goldsman
et al. (2002), Hong (2006) improve the performance but they still
use the Bonferroni's inequality, and so the methods are inefficient
when there are several systems. Procedures in Kim and Dieker (2011),
Dieker and Kim (2012) do not use the Bonferroni's inequality only
when compare groups of three alternatives.

Since the classic IZ procedures take too many samples with many alternatives,
these methods are unpopular when there are more than a few hundred
alternatives. However, Frazier (2014) presented a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), whose
lower bound on worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in the
discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of the most popular IZ procedures,
especially on problems with many alternatives. Unfortunately, the
proof that the BIZ procedure satisfies the IZ guarantee for the discrete-time
case assumes that variances are known and have an integer multiple
structure which is not very realistic. In practice, variances are
unknown. However, asymptotically we can use a central limit theorem
that allows us to prove the asymptotic validity of the BIZ procedure
for the discrete-time case. Moreover, we only need to assume that
the systems are independent, identically distributed and have finite
variance.

Kim et al. (2006) also proves the asymptotical validity of a IZ procedure.
Our proof is larger because the BIZ procedure is more sophisticated
and the bound for the PCS is tighter. To prove the case when the variances
are known, we use a theorem for Ergodic processes that shows how to
standardize the output data to make them behave like Brownian motion
processes in the limit. We also use an extension of the Continuous
Mapping Theorem (Theorem 5.5 of Billingsley 1968) to see that the
algorithm behaves like a sequential elimination IZ procedure with
a Brownian motion process instead of the standardized sum of the output
data in the limit, and then we use the results of the paper of Frazier
\cite{key-5} to prove the validity of this algorithm in the limit.
Finally, we use a random change of time argument to prove the case
when the variances are unknown.

This paper is organized as follows: In $\text{§}2$, we recall the
indifference-zone ranking and selection problem. In $\text{§}3$,
we recall the Bayes-inspired IZ (BIZ) procedure. In $\text{§}4$,
we present the proof of the validity of the algorithm when the variances
are known. In $\text{§}5$, we prove the case when the variances are
unknown. In $\text{§}6$, we present some simulations showing the
effectiveness of the algorithm. In $\text{§}7$, we conclude.

\section{Indifference-Zone Ranking and Selection }

Ranking and Selection is a procedure for selecting the best system
among a finite set of alternatives, i.e. the system with the largest
mean. The method selects a system as the best based on the samples
that are observed sequentially over the time. If the best system is
selected, we say that the procedure has made the \emph{correct selection}
(CS). We define the \emph{probability of correct selection} as 
\[
\mbox{PCS}\left(\mu,\lambda\right)=\mathbb{P}_{\mu,\lambda}\left(\hat{x}\in\mbox{arg max}_{x}\mu_{x}\right)
\]
where $\hat{x}$ is the alternative chosen by the procedure and $\mathbb{P}_{\mu,\lambda}$
is the probability measure under which samples from system $x$ have
mean $\mu_{x}$ and finite variance $\lambda_{x}^{2}$.

In the Indifference-Zone Ranking and Selection, the procedure is indifferent
in the selection of a system whenever the means of the populations
are nearly the same. Formally, let $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
be the vector of the true means, the \emph{indifference zone} is defined
as the set $\left\{ \mu\in\mathbb{R}^{k}:\mu_{\left[k\right]}-\mu_{\left[k-1\right]}<\delta\right\} $.
The complement of the indifference zone is called the \emph{preference
zone} (PZ) and $\delta>0$ is called the indifference zone parameter.
We say that a procedure meets the \emph{indifference-zone (IZ) guarantee
}at $P^{*}\in\left(1/k,1\right)$ and $\delta>0$ if
\[
\mbox{PCS}\left(\mu,\lambda\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
\]
We assume $P^{*}>1/k$ because IZ guarantees can be meet by choosing
$\hat{x}$ uniformly at random from among $\left\{ 1,\ldots,k\right\} $.

\section{The Bayes-inspired IZ (BIZ) Procedure}

BIZ is an elimination procedure. This procedure maintains a set of
alternatives that are in contention, and it takes samples from each
alternative in this set at each point in time. At beginning, all alternatives
are in contention, and over the time alternatives are eliminated.
The procedure ends when there is only one alternative in the contention
set and this remain alternative is chosen as the best.

Frazier (2014) showed that the BIZ procedure with known common variance
satisfies the IZ guarantee when the systems follow the normal distribution
, with tight bounds on worst-case preference-zone in continuous time.
He also proved that this procedure retains the IZ guarantee when the
systems follow the normal distribution, and the variances are known
and are integer multiples of a common value. The continuous time version
of this procedure also satisfies the IZ guarantee, with a tight worst-case
preference-zone PCS bound.

The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
variances is given in Alg. 2. It takes a variable number of samples
from each alternative, and $n_{tx}$ is this number. This algorithm
depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
and $n_{0}$. $n_{0}$ is the number of samples to use in the first
stage of samples, and $100$ is the recommended value for $n_{0}$.
$B_{x}$ controls the number of samples taken from system $x$ in
each stage.

For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
we define a function
\[
q_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
\]
where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.

\paragraph{Algorithm: Discrete-time implementation of BIZ, for unknown and/or heterogeneous variances.}    
\begin{algorithmic}[1]   
\label{alg:hetero-BIZ}   
\REQUIRE $c \in [0,\cmax]$, $\delta>0$, $P^*\in(1/k,1)$, $n_0\ge0$ an integer, $B_1,\ldots,B_k$ strictly positive integers.  Recommended choices are $c=\cmax$, $B_1=\cdots=B_k=1$ and $n_0$ between $10$ and $30$.     If the sampling variances $\lambda^2_x$ are known, replace the estimators     
$\lambdahat^2_{tx}$ with the true values $\lambda^2_x$, and set $n_0=0$.

\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.     
\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
\WHILE{$x\in\mbox{max}_{x\in A} q_{tx}\left(A\right)<P$}
\WHILE{$\mbox{min}_{x\in A} q_{tx}\left(A\right) \le c$}
 \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
    \STATE Let $\upthresh \leftarrow \upthresh/(1-q_{tx}\left(A\right))$.     
\STATE Remove $x$ from $A$.
\ENDWHILE
  \STATE Let $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.     
\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.     \STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.  Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.    
\STATE Increment $t$.
 \ENDWHILE
  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} Z_{tx} / n_{tx}$ as our estimate of the best.

@@

\vspace{10mm}
This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm 2 can be generalized to the continuous case (See appendix B and Frazier (2014)). This procedure is a slightly modification of the original BIZ procedure

@@

In this section we prove that the BIZ procedure satisfies the IZ guarantee
when the variances are known and $\delta\rightarrow0$, where the
vector of the true means $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
is equal to $\delta a$ for some $a\in\mathbb{R}^{k}$ and $\delta>0$.
Without loss of generality suppose that the true means satisfy that
$\mu_{k}>\mu_{k-1}\geq\cdots\geq\mu_{1}$. We suppose that samples
from system $x\in\left\{ 1\ldots,k\right\} $ are identically distributed
and independent, over time and across alternatives. We also define
$\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$
and we suppose that $\mbox{min}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}>0$
and $\mbox{max}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}<\infty$.

The BIZ procedure maps $\left(Y_{n_{x}\left(t\right),x}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
to a selection decision, where $Y_{n_{x}\left(t\right),t}$ is the
sum of samples observed by time $t$. In more detail, it works by
transforming $\left(Y_{n_{x}\left(t\right),x}:A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
to $\left(q'_{tx}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$.
This $q'$ process is given by time process with jumps at $t\in\mathbb{N}$,
\[
q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\right.
\]
where the variances are fixed. The same distribtuion over selection
decision will result if we apply the same same selection process to
the following time process with jumps at $t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} =\delta^{2}\mathbb{N}$,
\[
q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
\]
Later, we can approximate the previous process by the continuous time
process
\begin{eqnarray}
q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001}
\end{eqnarray}
where $t\geq0$ . Later we will show the difference in selection decisions
vanishes as $\delta\rightarrow0$.

After that, we would like to use a kind of central limit theorem for
$Z_{\frac{t}{\delta^{2}}x}=Y_{n_{x}\left(t/\delta^{2}\right),x}$
when $\delta$ goes to zero to work with a Brownian motion instead.
Specifically, we are going to see that the the standardized sum of
the output data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
which is the set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$
that are right-continuous and have left-hand limits, with the Skorohod
topology. The definition and the properties of this topology may be
found in Chapter 3 of Billingsley 1999 and the appendix. We will first
see this result because it will give us a clue for proving the asymptotic
validity of the Algorithm 2.

We briefly recall the definition of convergence of random paths in
the sense of $D_{\infty}$. Suppose that we have a sequence of random
paths $\left(\mathcal{X}_{n}\right)_{n\geq0}^{\infty}$ such that
$\mathcal{X}_{n}:\varOmega\rightarrow D_{\infty}$ where $\left(\Omega,\mathcal{F},\mathbb{P}\right)$
is our probability space. We say that $\mathcal{X}_{n}\Rightarrow\mathcal{X}_{0}$
in the sense of $D_{\infty}$ if $P_{n}\Rightarrow P_{0}$ where $P_{n}:\mathcal{D}_{\infty}\rightarrow\left[0,1\right]$
are defined as $P_{n}\left[A\right]=\mathbb{P}\left[\mathcal{X}_{n}^{-1}\left(A\right)\right]$
for all $n\geq0$ and $\mathcal{D}_{\infty}$ are the Borel subsets
for the Skorohod topology.

The following lemma shows that the standardized sum of the output
data with $t$ changed by $t/\delta^{2}$ converges to a Brownian
motion in the sense of $D_{\infty}$.

@@

For each $x\in\left\{ 1\ldots,k\right\} $, we define
\[
\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
\]
where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
$x$. Let $x\in\left\{ 1\ldots,k\right\} $, then
\[
\mathcal{C}_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right)
\]
as $\delta\rightarrow0$ in the sense of $D[0,\infty)$, where $W_{x}$
is a standard Brownian motion.

@@

By Theorem 19.1 of Billingsley 1999,

\[
\frac{Y_{n_{x}\left(t\right),x}-\mbox{floor}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right)
\]
in the sense of $D[0,\infty)$.

Fix $w\in\Omega$. Observe that
\[
\frac{Y_{\mbox{floor}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{floor}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}-\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\rightarrow0
\]
uniformly in $\left[0,s\right]$ for all $s\geq0$ and then by Theorem
A.2 
\[
\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right)
\]
in the sense of $D[0,\infty)$.

Since $\frac{\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}-ceil\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right)}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\rightarrow0$
uniformly on $[0,s]$ for every $s\geq0$, then by Theorem A.2

\[
\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right).
\]

Finally, observe that for fixed $\omega\in\Omega$,
\begin{eqnarray*}
 &  & \frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}-\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)+n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\right),x}-\mbox{}\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\\
 & = & \frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)+n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\right),x}+\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\\
 & \rightarrow & 0
\end{eqnarray*}
uniformly in $\left[0,t\right]$ for all $t\geq0$, and so by Theorem
A.2 the result follows.

@@

Now, we use the product topology in $D^{k}\left[0,\infty\right)$
for $k\in\mathbb{N}$. This topology may be described as the one under
which $\left(Z_{n}^{1},\ldots,Z_{n}^{k}\right)\rightarrow\left(Z_{0}^{1},\ldots,Z_{0}^{k}\right)$
if and only if $Z_{n}^{i}\rightarrow Z_{0}^{i}$ for all $i\in\left\{ 1,\ldots,k\right\} $.
See the Miscellany of Billingsley 1968. The following corollary follows
from the previous result and independence.

We have that
\[
\mathcal{C}\left(\delta,\cdot\right):=\left(\mathcal{C}_{x}\left(\delta,\cdot\right)\right)_{x\in A}\Rightarrow W\left(\cdot\right):=\left(W_{x}\left(\cdot\right)\right)_{x\in A}
\]
as $\delta\rightarrow0$ in the sense of $D_{\infty}^{k}$.\\
